Homework

### 2016-07-02 Macro Impacts.tex
Gauge invariance -- yay!
Just clarified one thing
Nevermind...
Imposed divergenceless gauge - obtained A_i
The important technique I used was to maintain proper symmetry of my
substitutions.

First observe that any three of these equations together forms a singular linear system.

@@

Taking the sum of the first two reveals that

@@

This, along with being traceless, shows that the shear only has two independent degrees of freedom: the polarizations. In other words, we have shown that you can always diagonalize the stress tensor.

@@

We now solve for $A_i$ in terms of $\Sigma_i$.
We still have a gauge degree of freedom...

>>>>

First observe that any three of these equations together forms a singular linear system in $A_i$. Thus we cannot invert to solve for $A_i$. However, we can get some information about the $\Sigma$'s.

@@

Taking the sum of the first two reveals that`

@@

This, along with being traceless, shows that the shear only has two independent degrees of freedom: the polarizations.

@@

It is impossible to solve for $A_i$ in terms of the stress as is, hence we must fix a gauge. To do this, we fix $\nabla\cdot a=0$, whence
0=k_xA_x+k_yA_y+k_zA_z\,.
From earlier, we have
-\Sigma_{zz}&=2k_z(k_x A_y-k_y A_x)\,,
which becomes
-\Sigma_{yy}&=2k_y\ps{-\f{k_z}{k_x} \p{k_yA_y+k_zA_z}-k_x A_z}\,,\\
-\Sigma_{zz}&=2k_z\ps{k_x A_y+\f{k_y}{k_x} \p{k_yA_y+k_zA_z}}\,,
which simplifies to
-\Sigma_{yy}&=-\f{2k_y}{k_x}\ps{k_y k_z A_y+\p{k_z^2+k_x^2} A_z}\,,\\
-\Sigma_{zz}&=\f{2k_z}{k_x}\ps{\p{k_x^2 + k_y^2}A_y+k_yk_zA_z}\,,
Hence
A_x&=\f{(k_y^2-k_z^2)(\Sigma_{yy}-\Sigma_{zz})+k_x^2(\Sigma_{yy}+\Sigma_{zz})}{2k_x^2k^2}\,,\\
&=\f{(k_y^2-k_z^2)(\Sigma_{yy}-\Sigma_{zz})-k_x^2\Sigma_{xx}}{2k_x^2k^2}\,,\\
&=\f{(k_y^2-k_z^2)}{k_x^2}\f{(\Sigma_{yy}-\Sigma_{zz})}{2k^2}-\f{\Sigma_{xx}}{2k^2}\,,\\
By symmetry, we have
A_x&=\f{(k_y^2-k_z^2)}{k_x^2}\f{(\Sigma_{yy}-\Sigma_{zz})}{2k^2}-\f{\Sigma_{xx}}{2k^2}\,,\\
A_y&=\f{(k_z^2-k_x^2)}{k_y^2}\f{(\Sigma_{zz}-\Sigma_{xx})}{2k^2}-\f{\Sigma_{yy}}{2k^2}\,,\\
A_z&=\f{(k_x^2-k_y^2)}{k_z^2}\f{(\Sigma_{xx}-\Sigma_{yy})}{2k^2}-\f{\Sigma_{zz}}{2k^2}\,.
Observe, in the case that all stresses are equal, we obtain that $A_x=A_y=A_z=0$, as we should.
